### 2023-04-10 main/chapter_theory.tex
paste some cross-section numbers

\subsubsection{Cross-sections}
A substantial production cross-section is a necessary condition for a process
to be observable with finite data.
The Run~2 dataset studied by our $\twoljets$ search comprises
$L = 139\,\mathrm{fb}^{-1}$
of proton-proton collisions, meaning that a process with production
cross-section $\sigma = 1\,\mathrm{fb}$
yields a Poisson mean of $\mu = L \sigma = 139$ events.
To achieve a mean of one event in the dataset,
below which it becomes exceedingly hard to observe,
a process needs a cross-section at least $1 / L \approx 7\,\mathrm{pb}$.

Cross-sections for the $\twoljets$ C1N2 and GMSB models are determined by two
factors: production cross-section and the decay branching fraction.
Each process pair-produces some heavy parent particles, so their production
cross-sections scale down with the parent particle mass
as both parton distribution hard-scatter matrix element
are pushed to harder scales.
For mass scale $q$, these three factors combine to an rapidly decaying scaling
of cross-section with parent mass, which goes very roughly like
$\sigma \sim q^{-6}$ in the several-hundred-$\,\eV[G]$ regime.
Example production cross-sections for similar models are displayed in
Figure~\ref{fig:theory_susy_xs}.
Branching fractions in decay further reduce the observable cross-sections in
our selected decay channels; however, these are constant factors that do not
scale with parent mass.

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/theory_pdg_susy_xsec.pdf}
\caption[
Cross-section scaling of some supersymmetric pair production modes
]{%
Cross-section scaling of some supersymmetric pair production modes
in models similar to the $\twoljets$ C1N2 and GMSB simplified models.
Note the similar scaling parent particle mass  for all gaugino and slepton
production modes shown;
this effect is due to fundamental properties of parton distribution functions
and scattering matrix-elements, and is not unique to supersymmetry.
These cross-sections do not include branching fraction factors, which are
needed to determine the C1N2 and GMSB cross-sections.
This figure is reproduced from~\cite{pdg2022ynf}.
\\[0.4em]
The label `wino` indicates that the gaugino mixtures mostly comprise the
superpartners of the $W$ fields, and `higgsino` indicates that they instead
comprise higgsino fields.
\\[0.4em]
Cross-sections below around $7\,\mathrm{pb}$ are expected to produce no
events in our $139\,\mathrm{fb}^{-1}$ of data.
}
\label{fig:theory_susy_xs}
\end{figure}

\TODO{example numbers}

>>>>

\subsubsection{Cross-sections}
A substantial production cross-section is a necessary condition for a process
to be observable with finite data.
The Run~2 dataset studied by our $\twoljets$ search comprises
$L = 139\,\mathrm{fb}^{-1}$
of proton-proton collisions, meaning that a process with production
cross-section $\sigma = 1\,\mathrm{fb}$
yields a Poisson mean of $\mu = L \sigma = 139$ events.

\begin{figure}[tp]
\centering
\includegraphics[width=0.98\textwidth]{figures/theory_pdg_susy_xsec.pdf}
\caption[
Cross-section scaling of some supersymmetric pair production modes
]{%
Cross-section scaling of some supersymmetric pair production modes
in models similar to the $\twoljets$ C1N2 and GMSB simplified models.
Note the similar scaling parent particle mass  for all gaugino and slepton
production modes shown;
this effect is due to fundamental properties of parton distribution functions
and scattering matrix-elements, and is not unique to supersymmetry.
These cross-sections do not include branching fraction factors, which are
needed to determine both C1N2 and GMSB model cross-sections.
The C1N2 model is wino-like, and the GMSB model is higgsino-like.
This figure is reproduced from~\cite{pdg2022ynf}.
\\[0.4em]
The label `wino` indicates that the gaugino mixtures mostly comprise the
superpartners of the $W$ fields, and `higgsino` indicates that they instead
comprise higgsino fields.
\\[0.4em]
Cross-sections below around $7\,\mathrm{pb}$ are expected to produce no
events in our $139\,\mathrm{fb}^{-1}$ of data.
}
\label{fig:theory_susy_xs}
\end{figure}

Cross-sections for the $\twoljets$ C1N2 and GMSB models are determined by two
factors: production cross-section and the decay branching fraction.
Each process pair-produces some heavy parent particles, so their production
cross-sections scale down with the parent particle mass
as both parton distribution hard-scatter matrix element
are pushed to harder scales.
For mass scale $q$, these three factors combine to an rapidly decaying scaling
of cross-section with parent mass, which goes very roughly like
$\sigma \sim q^{-6}$ in the several-hundred-$\,\eV[G]$ regime.
Production cross-sections for these models are displayed in
Figure~\ref{fig:theory_susy_xs};
in this figure,
cross-sections for the C1N2 model are correspond to those labelled
`$\chargino_1 \neutralino_2$ (wino)', and
cross-sections for the GMSB model are a little smaller, and correspond to those
labelled `$\tilde \chi \tilde \chi$ (higgsino)'.

Typical scenarios studied in $\twoljets$ parent masses ranging from
around $200\,\eV[G]$ to $800\,\eV[G]$ under both of its C1N2 and GMSB models.
The production cross-section for signals from its C1N2 model is
$1800\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $4.8\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$.
The production cross-section for signals from its GMSB model is
$1300\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $3.5\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$~\cite{
Fuks:2012qx,Fuks:2013vua}.
These values are rounded to two significant figures.
Cross-section uncertainties are shaded in  Figure~\ref{fig:theory_susy_xs},
but appear very small on its log scale;
the relative uncertainties increase with parent mass from about
$\pm 6\%$ at $m(\mathrm{parent}) = 200\,\eV[G]$.
to about
$\pm 12\%$ at $m(\mathrm{parent}) = 800\,\eV[G]$
in both models.

Although these cross-sections imply that several hundred signal events are
expected even at $m(\mathrm{parent}) = 800\,\eV[G]$, the raw number of signal
events does not mean that the signal is visible.
Visible signals must necessarily also be recorded as data,
distinguishable from Standard Model backgrounds.
Indeed, much of the work on a search like $\twoljets$ pertains to this
data selection and the separation of signals from backgrounds.
Furthermore, these are raw production cross-sections;
the yield of signal events that also decay into selected products is much
smaller ---
for starters, a $Z$ boson decays to electrons or muons with only around
$10\%$ branching fraction~\cite{pdg2022ynf}.
Such diversity in decay modes motivates the wide variety of targets in
\atlas's many SUSY searches.
